---
title: "Gun control Chi square"
author: "Eva Marrero"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Eva and I'm adding some text here to see if my collaborators can get this file.

=======
I'm Eva again, and I'm updating some text.

Im the collaborator adding text

Creator (Eva):

Getting the gc_vf data, loading the tidyverse, and getting some summary counts

```{r}
library(tidyverse)
gc_df <- read_csv("gc_df.csv")

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")

get_guns

```

Im the collaborator, Isabelle and I am going to do chi square. 

Question-

Is there a significant difference in gun controll perspectives (as related to acces to gun) for males and females? 
or
Is there a significant association between sex and gun control reccomendations? 
or
Is perception of gun control access indipendent of sex?


Chi-Square
```{r}

guns_prop<- prop.table(as.matrix(get_guns), 1)
guns_prop

# performing chi-square
guns_x2<-chisq.test(get_guns)
guns_x2




```

Ho no association
Ha there is an association 

Reccomeded government action on gun access differs significantl for males and females ($\chi^2$(`r guns_x2$parameter`) = ....,  p<0.001)





